Venn diagrams indicate erroneous analyses in transcriptomics

### 2022-01-16 presentation/venn_diagrams_weiner_2022_01_06.rmd
major rewrite

```{r fig3,dpi=300,dev="png"}
tmp <- merge(res.merged, res$full, by="ENSEMBL")
tmp <- tmp[ , c("DEG.g1", "DEG.g2", "DEG") ]
colnames(tmp) <- c("G1", "G2", "Full dataset")
plot(euler(tmp), quantities=list(type=c("counts", "percent")))
```

@@

```{r montecarlo,cache=TRUE,fig.width=7.5,fig.height=6.5}
## note: given that the monte carlo simulation is quite time consuming, we
## have included the code for it in another file, `montecarlo.R`. If trying
## to replicate this manuscript, please execute that file first to generate
## the necessary replicates.

@@

plot_grid(g1, g2, g3, g4, labels = LETTERS[1:4])
```

@@

>>>>

```{r fig3,width=5,height=5,dpi=300,dev="png"}
tmp <- merge(res.merged, res$full, by="ENSEMBL")
tmp <- tmp[ , c("DEG.g1", "DEG.g2", "DEG") ]
colnames(tmp) <- c("G1", "G2", "Full dataset")
plot(euler(tmp), quantities=list(type=c("counts", "percent")))
```

In a larger data set, majority of the "specific" genes are significant.

@@

 * Increase the sample size to have a higher sensitivity (fewer FNs)

 * Increase the LFC threshold to have fewer false positives

```{r montecarlo,cache=TRUE,fig.width=7.5,fig.height=5.5}
## note: given that the monte carlo simulation is quite time consuming, we
## have included the code for it in another file, `montecarlo.R`. If trying
## to replicate this manuscript, please execute that file first to generate
## the necessary replicates.

@@

plot_grid(g3, g4, labels = LETTERS[1:2])
```

@@

```{r montecarlo2,cache=TRUE,fig.width=7.5,fig.height=5}
plot_grid(g1, g2, labels = LETTERS[1:2])
```

## Thank you!

Source code for this presentation:
[https://github.com/bihealth/manuscript_venn_diagrams](https://github.com/bihealth/manuscript_venn_diagrams)

```{r}
library(qrcode)
plot(qr_code("github.com/bihealth/manuscript_venn_diagrams"))
```
